Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-18 BN_discretizer_paper.tex
Update Experiment section

\begin{figure}[ht]
  \centering
   \input{graph_autocar_1}
   \caption{The Bayesian network obtained with K2 on the prediscretized Auto MPG dataset}
  \label{fig:auto_graph_1}
\end{figure}

Table \ref{table:auto_disc_table_1} shows the numbers of intervals after discretization, the positions of discretization edges, and log-likelihood of 10-fold cross validation. For the Bayesian network in Fig. \ref{fig:auto_graph_1}, the approximation \ref{eq:opt_prob_approx} only reduces runtime and has no influence on discretization result. MDL principle discretization works not well, since it discretizes all variables with only one interval. The reason that the MDL method discretizes variables into too few number of intervals is discussed in Section \ref{subsec:discuss_exp}.

\begin{table}[h]
  \centering
  \caption{Discretization result of Auto MPG dataset based on the graph in Fig. \ref{fig:auto_graph_1}. The discretization policy for the heuristic matches that for the optimal Bayesian approach. The MDL method is less sensitive to distribution of values of other variables, thus it fails to return discretization edges.}
  \input{table_autoMPG_1.tex}
  \label{table:auto_disc_table_1}
\end{table}

@@

If the network structure is not known in advance, it should be learned along with the discretization process. Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization. This result is obtained by running Algorithm \ref{alg:structure_learn} fifty times and choosing the one with the highest K2 score.

@@

 %{\centering
%\begin{minipage}{0.50\textwidth}
  %\centering
  %\scalebox{0.7}{
  %\input{graph_autocar_2}}
  %\captionof{figure}{The learned discrete-\newline valued Bayesian network}
  %\label{fig:auto_graph_2}
%\end{minipage}
%\begin{minipage}{0.50\textwidth}
  %\raggedleft
  %\input{table_autoMPG_2.tex}
  %\captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
 % \label{Auto_MPG_disc_table_2}
%\end{minipage}
%}

Figure \ref{fig:auto_exp2_distr_1_3} compares the discretization edges of variable $A$ and $C$ in the learned network in Figure \ref{fig:auto_graph_2} with the raw data. Again, the black dots are raw data points. Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_exp2_distr_1_3} are less than Figure \ref{fig:auto_exp2_distr_1_3}, they still have a good capture of raw data distribution. This indicated that although the discretization result of the optimal Bayesian approach might vary according to the network structure, it still preserves the quality of discretization.

\begin{figure}[ht]
      \input{graph_auto_exp2_distr_1_3}
  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ of the learned network in Figure \ref{fig:auto_graph_2}. Although the number of discretization edges is less than in Figure \ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
  \label{fig:auto_exp2_distr_1_3}
\end{figure}

@@

The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 a thousand times. Table \ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood, although the latter returns non-trivial result in this experiment. Note that the
heuristic method discretizes variable $G$, $H$ and $J$ into one more interval than the optimal Bayesian approach, and has less number of intervals on variable $M$. Although the heuristic method has more intervals after discretization on all variables, it does not lead to a higher likelihood result. This can be interpreted as that the extra discretization edges on $G$, $H$ and $J$ are less necessary and the losing discretization edge on $M$ is important. On the other hand, if running time is a concern, then the heuristic method can be considered a better approach in this case, since its discretization result is nearly as good as the result of the optimal Bayesian approach.

Notice that there are some discretization edges shown in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$. This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find other edges.

\begin{figure}[ht]
  \centering
      \input{graph_wine_1}
  \caption{\tim{Structure from prediscretized K2 structure learning to compare the methods}}
  \label{fig:wine_graph_1}
\end{figure}

\begin{table}
  \centering
  \scalebox{1.0}{
  \input{table_wine_1.tex}
  }
  \caption{Discretization result of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1}. The optimal Bayesian approach has the best discretization result in terms of likelihood. The heuristic method obtains a result nearly as good as the Bayesian approach. The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals. Some discretization edges are obtained by all three methods.
  \todo{MDL has bins, heuristic is slightly worse in logl but still good. MDL keeps all of its CPDs small, no neighboring vars both have more than 1 interval.}
  \tim{Should we scale the logl? What is the best way to do that?}
  }
  \label{table:wine_disc_table_1}
\end{table}

Figure \ref{fig:wine_exp1_distr} compares the discretization results by the proposed method and the MDL method. It shows the discretization edges on variable $E$ and $K$, and the probability of resulting discretized area. The proposed method has more discretization edges than the MDL method. Furthermore, the discretization edges on $E$ and $K$ obtained by the MDL method are either included in or close to the edges by obtained proposed method. This indicates that the proposed method can include the discretization result obtained by the MDL method and meanwhile, capture other discretization edges without significantly increase cardinality numbers of variables.

%\begin{figure}[ht]
%  \centering
%    \input{graph_wine_exp1_distr}
%  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the proposed method and the MDL method}
%  \label{fig:wine_exp1_distr}
%\end{figure}

@@

Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} fifty times. The integer numbers next to variables are cardinality numbers of variables. By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by Algorithm \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm. Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{table:wine_disc_table_1}.

Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$. The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{fig:wine_exp1_distr}. This indicates that some discretization edges are robust against the network structure.

@@

\begin{figure}[ht]
  \centering
  \begin{tabular}{cc}
    \input{graph_wine_exp2_distr_5_11}
 \end{tabular}
  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}
  \todo{Note unchanged discretization edge.}
  }
  \label{fig:wine_exp2_distr}
\end{figure}

@@

In this subsection, another two experiments are conducted on the Housing dataset from the Irvine repository \citep{Lichman_2013}. This dataset has 506 instances and 14 variables. Only variables $D$ and $I$ are discrete-valued with cardinality numbers 2 and 9, respectively. Again, in the first experiment, the network structure is given. In the second experiment, the network structure is not provided.

@@

The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score. Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables. MDL method does not discretize most variables. The proposed method with the approximation discretizes variables into too many intervals. For example, it discretized $J$ into 58 intervals. The proposed method without the approximation has a good control of number of intervals.
\begin{figure}[ht]
  \centering
  \begin{tabular}{cc}
   \input{graph_housing_1}
   \end{tabular}
  \caption{\todo{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}}
  \label{fig:housing_graph_1}
\end{figure}

\begin{table}
  \centering
  \scalebox{1.0}{
  \input{table_housing_1.tex}
  }
  \caption{Discretization result of Housing dataset based on the graph Figure~\ref{fig:housing_graph_1} \tim{Fig. vs. Figure}}
  \label{table:housing_disc_table_1}
\end{table}

Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result by the propose method on the network in Figure~\ref{fig:housing_graph_1}.
In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$. These repeating values cause the high number of intervals after discretization for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area. On the other hand, there is no such over-repeated values of the raw data on variable $H$. Thus, the numbers of intervals after discretization for variable $E$ remains normal, as what we have seen in previous datasets.

\begin{figure}[ht]
    % \begin{tabular}{cc}
      \input{graph_housing_exp1_distr_3_5}
    % \end{tabular}
  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}}
  \label{fig:housing_exp1_distr_3_5}
\end{figure}

\begin{figure}[ht]
     %\begin{tabular}{cc}
    \input{graph_housing_exp1_distr_8_5}
     %\end{tabular}
  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}}
  \label{fig:housing_exp1_distr_8_5}
\end{figure}

@@

\begin{figure}[ht]
    % \begin{tabular}{cc}
      \input{graph_housing_2}
    % \end{tabular}
  \caption{The learned discrete-valued Bayesian network from the Housing dataset
  \todo{Mention that there are high-cardinality vars.}
  \tim{Var with 1 interval?}
  }
  \label{fig:housing_graph_2}
\end{figure}

Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
Although the number of intervals after discretization on $H$ is not big, it captures the distribution of the raw data along with the discretization edges on $E$.

\begin{figure}[ht]
     %\begin{tabular}{cc}
      \input{graph_housing_exp2_distr_3_5}
     %\end{tabular}
  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}}
  \label{fig:housing_exp2_distr_3_5}
\end{figure}

\begin{figure}[ht]
    % \begin{tabular}{cc}
      \input{graph_housing_exp2_distr_8_5}
    % \end{tabular}
  \caption{The discretization result on variable $H$ and $G$ of the network in Figure~\ref{fig:housing_graph_2}}
  \label{fig:housing_exp2_distr_8_5}
\end{figure}

@@

>>>>

\begin{figure}[ht]
  \centering
   \input{graph_autocar_1}
   \caption{Structure from prediscretized K2 structure learning to compare the methods for Auto MPG dataset}
  \label{fig:auto_graph_1}
\end{figure}

Table \ref{table:auto_disc_table_1} shows the positions of discretization edges, and log-likelihood of 10-fold cross validation by three discretization methods. For the Bayesian network in Fig. \ref{fig:auto_graph_1}, the approximation \ref{eq:opt_prob_approx} only reduces runtime and has no influence on discretization result. MDL principle discretization works not well, since it discretizes each continuous variable by only one interval. The reason that the MDL method discretizes variables into too few number of intervals is discussed in Section \ref{subsec:discuss_exp}.

\begin{table}[h]
  \centering
  \caption{Discretization results of Auto MPG dataset based on the graph in Fig. \ref{fig:auto_graph_1} by the three methods. The first to fifth row are discretization edges on each continuous variable. The sixth row is the log-likelihood of the dataset based on the discretization results. The discretization result for the heuristic matches that for the optimal Bayesian approach. The MDL method is less sensitive to distribution of values of other variables and fails to return discretization edges.}
  \input{table_autoMPG_1.tex}
  \label{table:auto_disc_table_1}
\end{table}

@@

If the network structure is not known in advance, it should be learned along with the discretization process. Figure \ref{fig:auto_graph_2} show a learned discrete-valued Bayesian network and the corresponding numbers of intervals after discretization for each continuous variable. This result is obtained by running Algorithm \ref{alg:structure_learn} fifty times (without the approximation) and choosing the one with the highest K2 score.

@@

Figure \ref{fig:auto_exp2_distr_1_3} shows the discretization edges on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2} along with the raw data. Again, the black dots are raw data points. The colors of discretized areas are the corresponding maginalized probability. Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_exp2_distr_1_3} are less than Figure \ref{fig:auto_exp2_distr_1_3}, they still have a good capture of raw data distribution. This indicates that although the discretization result of the optimal Bayesian approach might vary according to the network structure, it still preserves the quality of discretization.

\begin{figure}[ht]
      \input{graph_auto_exp2_distr_1_3}
  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ in Figure \ref{fig:auto_graph_2}. Although the number of discretization edges is less than in Figure \ref{fig:auto_exp1_distr_1_3}, it still matches the raw data distribution very well.}
  \label{fig:auto_exp2_distr_1_3}
\end{figure}

@@

The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 a thousand times. Table \ref{table:wine_disc_table_1} shows a comparison between the optimal Bayesian approach and the MDL principle discretization method.
The discretization result obtained by the optimal Bayesian approach is better than the MDL discretization method in terms of likelihood. The heuristic method discretizes variable $G$, $H$ and $J$ into one less interval than the optimal Bayesian approach, and has one more number of intervals on variable $M$.
Although it returns different numbers of intervals and different positions of discretization edges with the optimal Bayesian approach, it still has a good discretization result in terms of likelihood. Furthermore, if running time is the main concern, the heuristic method can be considered a better approach in this case.

Notice that there are some discretization edges appearing in all three discretization methods, such as \num{1.42} and \num{2.35} on variable $C$ and \num{0.785} on variable $L$. This indicates that MDL indeed can find some important discretization edges, but it is not sensitive enough to find more edges.

\begin{figure}[ht]
  \centering
      \input{graph_wine_1}
  \caption{Structure from prediscretized K2 structure learning to compare the methods for Wine dataset}
  \label{fig:wine_graph_1}
\end{figure}

\begin{table}
  \centering
  \caption{Discretization results of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1} by the three different method. The first to the thirteenth row are discretization edges on each continuos variable. The fourteenth row is the log-likelihood of the dataset based on the discretization results. The optimal Bayesian approach has the best discretization result in terms of likelihood. The heuristic method obtains a result nearly as good as the Bayesian approach. The MDL method discretizes more than half of continuous variables but still does not discretize enough intervals. Some discretization edges appear in the results of all three methods, and indicate that they are the most determinant edges.}
  \scalebox{1.0}{
  \input{table_wine_1.tex}
  }
  \label{table:wine_disc_table_1}
\end{table}

Figure \ref{fig:wine_exp1_distr} compares the discretization results by the optimal Bayesian approach and the MDL method. The discretization edges \num{17.9} on $E$ and \num{34.6} on $K$ appear in both plots. This indicates that they are more necessary than other discretization edges on $E$ and $K$. On the other hand, the edge \num{23.25} on $E$ is also meaningful. For instance, after having an extra edge at \num{23.25}, the area from $E = 17.9$ to $30$ is divided two rectangles such that the one from $E=17.9$ to $23.25$ has relatively higher probability than $E=23.25$ to $30$. The MDL method does not capture this edge due to its low sensitivity toward distribution. For more discussion about the sensitivity, see Section \ref{subsec:discuss_exp}.

\begin{figure}[ht]
  \centering
    \input{graph_wine_exp1_distr}
  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the optimal Bayesian approach and the MDL method}
  \label{fig:wine_exp1_distr}
\end{figure}

@@

Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} fifty times. The integer numbers next to variables are cardinality numbers of variables. By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by Algorithm \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm. This is sensible, since when a network is learned along with discretization, variables have more freedom, by adjusting discretization edges, to construct the correlations with other variables and thus have more edges in the network.

Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$. The discretization edge at \num{17.9} on variable $E$ also appers in Figure \ref{fig:wine_exp1_distr}. This indicates that some discretization edges are robust against the network structure. Furthermore, in Figure \ref{fig:wine_exp2_distr}, the discretization edge at \num{23.5} on $E$ is lost. This is due to the number of parents of $E$ in Figure \ref{fig:wine_graph_2} is twice as in \ref{fig:wine_graph_1}. Usually, if a variable has more parents, then less number of intervals after discretization it has, since the information from parents are adulterated together.

@@

\begin{figure}[ht]
  \centering
  \begin{tabular}{cc}
    \input{graph_wine_exp2_distr_5_11}
 \end{tabular}
  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}. The discretization edge \num{17.9} on $E$ also appear in \ref{fig:wine_exp1_distr}. This indicates that some discretization edges are robust again the network structure.}
  \label{fig:wine_exp2_distr}
\end{figure}

@@

In this subsection, another two experiments are conducted on the Housing dataset from the Irvine repository \citep{Lichman_2013}. This dataset has 506 instances and 14 variables. Only variables $D$ and $I$ are discrete-valued with cardinality numbers 2 and 9, respectively. Again, in the first experiment, the network structure is given in advance. In the second experiment, the network structure is not provided in advance.

@@

The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score. Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables and also the log-likelihood of the dataset based on the discretization results. MDL method again does not discretize most variables. The heuristic method discretizes variables into too many intervals due to repeated values in the dataset, as we will see in later discussion. The optimal Bayesian approach has a good control of number of intervals. These numbers of intervals returned by the three methods illustrate that the heuristic method is over sensitive and the MDL method is less sensitive. The properties of sensitivity of the three algorithms will be discussed in Section \ref{subsec:discuss_exp}. On the other hand, although the heuristic method leads to high number of intervals, its corresponding log-likelihood on the dataset is not significantly better than the optimal Bayesian approach. This shows that the optimal Bayesian approach captures the important discretization edges.

\begin{figure}[ht]
  \centering
  \begin{tabular}{cc}
   \input{graph_housing_1}
   \end{tabular}
  \caption{Structure from prediscretized K2 structure learning to compare the methods for Housing dataset}
  \label{fig:housing_graph_1}
\end{figure}

\begin{table}
  \centering\caption{Discretization result of Housing dataset based on the graph in Figure~\ref{fig:housing_graph_1}. The first twelve rows show the numbers of intervals after discretization by the three method. The thirteenth row is the log-likelihood of the dataset based on the discretizatio results. The heuristic method is over sensitive and discretizes some variables into too many intervals. The MDL method is less sensitive and discretizes most variables by only one interval. The optimal Bayesian approach has a good control on number of intervals. \tim{Fig. vs. Figure}}
  \scalebox{1.0}{
  \input{table_housing_1.tex}
  }

  \label{table:housing_disc_table_1}
\end{table}

Figure~\ref{fig:housing_exp1_distr_3_5} and Figure~\ref{fig:housing_exp1_distr_8_5} show the discretization result of the optimal Bayesian approach on the network in Figure~\ref{fig:housing_graph_1}.
In Figure~\ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$. These repeating values cause the high number of intervals for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area. On the other hand, there is no such over repeated values of the raw data on variable $H$. Thus, the numbers of intervals after discretization for variable $H$ remains normal, as what we have seen in previous datasets.

\begin{figure}[ht]
    % \begin{tabular}{cc}
      \input{graph_housing_exp1_distr_3_5}
    % \end{tabular}
  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}. The scatter points are jittered due to the repeated values in the dataset. Furthermore, these repeated values lead to high number of discretization edges, since repeated values can easily form discretized areas by their own.}
  \label{fig:housing_exp1_distr_3_5}
\end{figure}

\begin{figure}[ht]
     %\begin{tabular}{cc}
    \input{graph_housing_exp1_distr_8_5}
     %\end{tabular}
  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_1}. Data points are not over repeated on $H$, thus the number of edges on $H$ remains desirable.}
  \label{fig:housing_exp1_distr_8_5}
\end{figure}

@@

\begin{figure}[ht]
    % \begin{tabular}{cc}
      \input{graph_housing_2}
    % \end{tabular}
  \caption{The learned discrete-valued Bayesian network from the Housing dataset. Variables $C$, $E$, $J$, $K$ have high numbers of intervals after discretization, since they are in a Markov blanket.
  \tim{Var with 1 interval?}
  }
  \label{fig:housing_graph_2}
\end{figure}

Figure~\ref{fig:housing_exp2_distr_3_5} and Figure~\ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure~\ref{fig:housing_graph_2}.
Again, variable $C$ and $E$ have many discretization edges due to the repeated values.
Although the number of intervals after discretization on $H$ is not large, it captures the distribution of the raw data along with the discretization edges on $E$.

\begin{figure}[ht]
     %\begin{tabular}{cc}
      \input{graph_housing_exp2_distr_3_5}
     %\end{tabular}
  \caption{The discretization result on variable $C$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}. The high number of discretization edges is due to the repeated values on the dataset in variable $C$ and $E$.}
  \label{fig:housing_exp2_distr_3_5}
\end{figure}

\begin{figure}[ht]
    % \begin{tabular}{cc}
      \input{graph_housing_exp2_distr_8_5}
    % \end{tabular}
  \caption{The discretization result on variable $H$ and $E$ of the network in Figure~\ref{fig:housing_graph_2}. Although the number of discretization edges on $H$ is not as large as $E$'s, they still match the distribution of the raw data very well.}
  \label{fig:housing_exp2_distr_8_5}
\end{figure}

@@

\begin{figure}[ht]
    % \begin{tabular}{cc}
      \input{graph_exp_discuss}
    % \end{tabular}
  \caption{A simple Bayesian network that is used to demonstrate the sensitivity of the three methods}
  \label{fig:exp_discuss}
\end{figure}

To quantatively discuss the sensitivity of the three methods, consider the Bayesian network in Figure \ref{fig:exp_discuss}, where $X$ is continuous-valued and $P_1$ and $P_2$ is discrete-valued. Let $P = \{  P_1, P_2 \}$. Assume $D_X = \{1.0,2.0,3.0, \ldots N \}$. Therefore, the corresponding objective functions to discretize $X$ in the three methods are:
\begin{equation}
\begin{aligned}
\text{Obj}_{\text{MDL}} & = Z_1 \cdot k + \log(N) \cdot \sum^k_{i=1} \sum^{J_P}_{j=1} I(a^*_i, (p_1,p_2)_j) \\
\text{Obj}_{\text{Bayesian}} &= Z_2 \cdot k + \log {{n_i + J_P - 1}\choose{J_P -1}} + \sum^k_{i=1} \log \left(   {{n_i !}\over{n^{(P)}_{i,1}! n^{(P)}_{i,2}! \cdots n^{(P)}_{i,J_P}!    }} \right) \\
\text{Obj}_{\text{Heuristic}} &= Z_2 \cdot k + \log {{n_i + J_{P_1} - 1}\choose{J_{P_1} -1}} + \log {{n_i + J_{P_2} - 1}\choose{J_{P_2} -1}} +\\
& \sum^k_{i=1}  \left[ \log \left(   {{n_i !}\over{n^{(P_1)}_{i,1}! n^{(P_1)}_{i,2}! \cdots n^{(P_1)}_{i,J_{P_1}}    }} \right)  + \log \left(   {{n_i !}\over{n^{(P_2)}_{i,1}! n^{(P_2)}_{i,2} \cdots n^{(P_2)}_{i,J_{P_2}}    }} \right) \right]
\end{aligned}
\end{equation}
